Analysis of Prenatal Depression and Anxiety during Covid-19

### 2024-03-25 outputs/paper.qmd
correct some captions

# Results {#sec-results}
```{r}
#| message: false
#| echo: false
#| warning: false
#| label: tbl-depression_model
#| tbl-cap: Estimating Prenatal Depression given Age, Household Income, Month of Delivery and Choice of Language
modelsummary(
  list(
    "Level of Depression" = depression_model))
```

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: tbl-anxiety_model
#| tbl-cap: Estimating Prenatal Anxiety given Age Group, Household Income, Month of Delivery and Choice of Language.
modelsummary(
  list(
    "Level of Anxiety" = anxiety_model))
```

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-depression_interval
#| fig-cap: The Coefficients and Confidence Interval in the Depression Model
modelplot(depression_model, conf_level = 0.95, color = 'royalblue3') +
  labs(x = "95% Level of Depression Interval")
```

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-anxiety_interval
#| fig-cap: The Coefficients and Confidence Interval in the Anxiety Model
modelplot(anxiety_model, conf_level = 0.95, color = 'indianred3') +
  labs(x = "95% Level of Anxiety Interval")
```

@@

```{r}
#| label: fig-weight_delivery
#| fig-cap: Distribution of Birth Weight and Length and Prenatal Mental Health by Delivery Mode
#| echo: false
#| warning: false
#| message: false
#| layout-ncol: 2
#| fig-subcap: ["Distribution of Birth Weight and Depression by Delivery Mode", "Distribution of Birth Weight and Anxiety by Delivery Mode", "Distribution of Birth Length and Depression by Delivery Mode", "Distribution of Birth Length and Anxiety by Delivery Mode"]
clean_data |>
  ggplot(aes(x = EPDS, y = birth_weight, color = delivery_mode)) +
  geom_smooth(method = "lm")+
  theme_minimal() + labs(x = "The Level of Prenatal Depression", y = "Birth Weight (grams)")

>>>>

# Results {#sec-results}
```{r}
#| message: false
#| echo: false
#| warning: false
#| label: tbl-depression_model
#| tbl-cap: Estimating Prenatal Depression given Age, Household Income, Education Level and Choice of Language
modelsummary(
  list(
    "Level of Depression" = depression_model))
```

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: tbl-anxiety_model
#| tbl-cap: Estimating Prenatal Anxiety given Age Group, Household Income, Education Level and Choice of Language.
modelsummary(
  list(
    "Level of Anxiety" = anxiety_model))
```

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-depression_interval
#| fig-cap: The Coefficients and Confidence Interval in the Depression Model
modelplot(depression_model, conf_level = 0.95, color = 'royalblue3') +
  labs(x = "Estimating Depression and 95% Confidence Interval")
```

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-anxiety_interval
#| fig-cap: The Coefficients and Confidence Interval in the Anxiety Model
modelplot(anxiety_model, conf_level = 0.95, color = 'indianred3') +
  labs(x = "Estimating Anxiety and 95% Confidence Interval")
```

@@

```{r}
#| label: fig-weight_length_delivery
#| fig-cap: Distribution of Birth Weight and Length and Prenatal Mental Health by Delivery Mode
#| echo: false
#| warning: false
#| message: false
#| layout-ncol: 2
#| fig-subcap: ["Distribution of Birth Weight and Depression by Delivery Mode", "Distribution of Birth Weight and Anxiety by Delivery Mode", "Distribution of Birth Length and Depression by Delivery Mode", "Distribution of Birth Length and Anxiety by Delivery Mode"]
clean_data |>
  ggplot(aes(x = EPDS, y = birth_weight, color = delivery_mode)) +
  geom_smooth(method = "lm")+
  theme_minimal() + labs(x = "The Level of Prenatal Depression", y = "Birth Weight (grams)")
